---
title: "Assignment 1"
author: "Longhao Chen"
date: "September 12, 2018"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Document assignment


Consider the following situation:  

A sloppy printer produces books with an average of 2 misprints per page. You want to
know how many pages have more than k misprints in a book of n pages. Make an n x k table that shows the relationship between the total number of pages in a book and the number of pages with k misprints.

Show and explain your work.  Include equations and calculations to teach the reader how to solve the problem.  Include an image of a book.

Push your solution to a github repository and submit the url for repository on blackboard.
Be sure your repo includes your document as a pdf file and as an RMD file.  Include other files needed to recompile your document.

```{r}
options(digits=2)
k<-vector(mode="numeric",length=0)
result<-rep(NULL,51)
p<-ppois(q = 0:10, lambda=2, lower.tail = FALSE) #Find out the possibility of more than k misprints and asign it to p
for (i in 1:11) {
  for (n in 1:51) {
    p1<-p[i] #Assign each probability of more than k misprints to p1
    k[n]<-pbinom(q = n, size = 50,prob = p1) #Figure out the binomial probability for different n pages
  }
  result<-rbind(result,k)
}

table<-as.data.frame(result)
table

colnames(table)=paste(0:50,"pages",sep="")
```


The approach to this problem starts with a simple poisson distribution, we are interested in figuring out the probability of misprints for each value of more than k misprints. Notice that we set lower.tail to FALSE because we are interested in the probability of more than k instead of leass than k. Then we need to plug in the probability from poisson distribution into each binomial distribution for different values of n.

Here is the equation of poisson distribution and binomial distribution

$P_x=e^{-\lambda}\frac{\lambda^k}{k!}$

$\sum_{i=0}^{k}\binom{n}{i}p^i(1-p)^{n-i}$



Here is a picture of the book

\begin{center}
\includegraphics{book}
\end{center}
